Internet Attribute Certificate Profile for Authorization (RFC5755) - A Cryptographic Analyses

### 2013-05-29 paper.tex
Explained few example uses

\subsection{Examples of usage}
when used? --> auth, data origin auth, non-repudiation

>>>>

\subsection{Examples of usage}
An AC can be used in different security related services. "As an example it could also be used to certify authorization information related to a public key. More specifically, it may be used to limit the liability resulting from a digital signature, or to constrain the usage of a public key (e.g., transaction of a limited value, certain time windows, etc.)."~\cite{tilborg2011encyclopedia}.

Different default attributes have been proposed, some of which are listed below.~\cite{benantar2006access,rfc_ac}
\begin{itemize}
	\item \textit{Service Authentication Information}, which identifies the AC holder to the service by name, with optional service-specific authentication information. This attribute could, by using some encryption scheme, also include the holder's identity and password.
	\item \textit{Charging identity}, which is used to charge the holder for the use of services.
	\item \textit{Role}, which is used to specify the role the holder has within a specific service.
	\item \textit{Clearance}, which defines the clearance the holder has for specific information (secret, top-secret, etc.).
	\item \textit{Group}, which describes the group the holder belongs to.
\end{itemize}

when used? --> auth, data origin auth, non-repudiation
